Bow shocks, bow waves, and dust waves. IV. Bow shape statistics

### 2019-04-02 papers/Papers1234/sec-quadrics-observations.tex
More improvements for Paper IV

\begin{figure}
  \centering
  \setlength\tabcolsep{0pt}
  \begin{tabular}{ll}
    (a) & (b) \\
    \includegraphics[height=1.167\linewidth]
    {figs/mipsgal-boxplot-Rc-R90-versus-R0}
        & \includegraphics[height=1.167\linewidth]
          {figs/mipsgal-boxplot-Rc-R90-versus-H0}
  \end{tabular}
  \caption{(a) Box plots of the distributions of bow shock shape
    parameters, \(R_c/R_0\) and \(R_{90} / R_0\), together with a
    measure of the tail asymmetry, \(|R_{90+} - R_{90-}| / R_{90}\),
    after partitioning on the bow shock size, \(R_0\).  All 3-, 4-,
    and 5-star sources are sorted according to \(R_0\) and divided
    into 5 non-overlapping sub-samples of roughly equal size, each
    labelled by their median value of \(R_0\) in arcseconds, as
    illustrated in the lower panel.  The colored boxes show the
    interquartile range, with the median indicated by a horizontal
    line, the 1st-to-9th interdecile range by error bars, and outliers
    by diamonds.  A 5-sample Anderson--Darling test and Brown--Forsythe
    test is performed for each dependent variable, with resultant
    \(p\)-value given at the bottom of each panel.   It is apparent
    that the dispersion in \(R_{90} / R_0\) (upper panel) increases
    systematically with \(R_0\), although the central value is roughly
    constant.  No clear systematic changes are apparent in
    \(R_c / R_{90}\) (middle panel).  (b)~As (a), but partitioning on
    the extinction-corrected \(H\)-band magnitude, \(H_0\).  Note that
    sub-samples are plotted in order of \textit{decreasing} magnitude
    to allow comparison between (a) and (b), given the negative
    correlation between \(H_0\) and \(R_0\) (see
    Fig.~\ref{fig:mipsgal-pairplot}).}
  \label{fig:mipsgal-boxplot}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
  \caption[]{Comparison of bow shock shapes between Herschel RSG/AGB
    arcs (large red symbols and hollow red contours) and MIPSGAL OB
    star arcs (small purple symbols and filled purple contours).
    Other details of the plots are as in
    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
    except that the diagnostic plots are zoomed in slightly to show
    more detail, and a smaller KDE smoothing bandwidth of
    \(0.12 \times 0.08\) is used.}
  \label{fig:herschel-compare-mipsgal}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
  \caption[]{Comparison of Orion with OB stars.  Other details of the
    plots are as in Figs.~\ref{fig:mipsgal-shapes}
    and~\ref{fig:mipsgal-uncorrelated}, except that the diagnostic
    plots are zoomed out to encompass larger ratio values, and a
    larger KDE smoothing bandwidth of \(0.3 \times 0.2\) is used.}
  \label{fig:ll-compare-mipsgal}
\end{figure*}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]
  {figs/mipsgal-boxplot-Rc-R90-versus-R0}
  \caption{Box plots of the distributions of bow shock shape
    parameters, \(\Pi\) and \(\Lambda\), together with a
    measure of the tail asymmetry, \(|\Lambda_{+} - \Lambda_{-}| / \Lambda\),
    after partitioning on the bow shock size, \(R_0\).  All 3-, 4-,
    and 5-star sources are sorted according to \(R_0\) and divided
    into 5 non-overlapping sub-samples of roughly equal size, each
    labelled by their median value of \(R_0\) in arcseconds, as
    illustrated in the lower panel.  The colored boxes show the
    interquartile range, with the median indicated by a horizontal
    line, the 1st-to-9th interdecile range by error bars, and outliers
    by diamonds.  A 5-sample Anderson--Darling test and Brown--Forsythe
    test is performed for each dependent variable, with resultant
    \(p\)-value given at the bottom of each panel.   It is apparent
    that the dispersion in \(\Lambda\) (upper panel) increases
    systematically with \(R_0\), although the central value is roughly
    constant.  No clear systematic changes are apparent in
    \(\Pi\) (middle panel).}
  \label{fig:mipsgal-boxplot}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
  \caption[]{Comparison of bow shock shapes between Herschel RSG/AGB
    arcs (large red symbols and hollow red contours) and MIPSGAL OB
    star arcs (small purple symbols and filled purple contours).
    Other details of the plots are as in
    Figs.~\ref{fig:mipsgal-shapes} and~\ref{fig:mipsgal-uncorrelated},
    except that the diagnostic plots are zoomed in slightly to show
    more detail, and a smaller KDE smoothing bandwidth of
    \(0.12 \times 0.08\) is used.}
  \label{fig:herschel-compare-mipsgal}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
  \caption[]{Comparison of Orion with OB stars.  Other details of the
    plots are as in Figs.~\ref{fig:mipsgal-shapes}
    and~\ref{fig:mipsgal-uncorrelated}, except that the diagnostic
    plots are zoomed out to encompass larger ratio values, and a
    larger KDE smoothing bandwidth of \(0.3 \times 0.2\) is used.}
  \label{fig:ll-compare-mipsgal}
\end{figure}
